Measuring Software Ticket Quality using Statistical Analysis

### 2018-04-17 paper/paper.tex
Refactor the tex file for the paper
Add title and reformat intro page
Create skeleton for the whole paper with sections in the right places

%% example.tex
%% Jeremy Singer
%% 16 Oct 12

@@

\title{An Example Paper for MSci Submission}
\author{Jeremy Singer}
\matricnum{12345678}

@@

\begin{abstract}
According to Simon Peyton Jones, an abstract should address
four key questions. First, what is the problem that this
paper tackles? Second, why is this an interesting problem?
Third, what is the solution this paper proposes?
Finally, why is the proposed solution a good one??
\end{abstract}

@@

\section{Background}

@@

\section{The WizWoz System}

@@

\section{Evaluation}

@@

@@

The standard Lorem Ipsum passage, used since the 1500s

``Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.''
\vskip8pt \noindent
{\bf Acknowledgments.}
This is optional; it is a location for you to thank people

\bibliographystyle{abbrv}
\bibliography{example}

>>>>

@@

\title{Measuring Software Ticket Quality using Statistical Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{2147392}

@@

\begin{abstract}

\end{abstract}

@@

\section{Related Work}

@@

\section{Building the Data Set}

@@

\section{Characterising the Data Set}

@@

\section{Correlations}

\section{Future Work}

@@

\vskip8pt \noindent
{\bf Acknowledgments.}
Tim, my parents, Corina.

\bibliographystyle{abbrv}
\bibliography{paper}
